### 2023-12-11 main.tex
''

		%This is slightly more general than \eqref{reversibilityCondition}.

@@

{\color{blue} \begin{remark}
	In the following, with a slightly abuse of notation, we denote the configuration vectors on the extra-site $u(x)$ by $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$. This allows to recall that these vectors belongs to the extra-space $N_{0}^{N-1}$ "attached" to original configuration space $\Omega$. Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}.

@@

@@

where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed in $0$.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have

@@

\todo{here Y instead of $\tau$?}

@@

Therefore, we compute the third cumulant, i.e. the three-point connected correlation as 
\begin{align}
	&\mathbb{E}\left[\left(\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{Y_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\left(\mathbbm{1}_{\{Y_{x_{3}}=a_{3}\}}-\langle\rho_{a_{3}}^{x_{3}}\rangle \right)\right]\nonumber\\
	=&-\frac{2x_{1}(L+1-2x_{2})(L+1-x_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt
\end{align}
\todo{should this all be $Y$ in the identities?}
\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with those found in Section 4.3 of \cite{vanicat2017exact}.
	\end{remark}

@@

	\todo{added ref... What about Section 4.4.5?}

@@

Observing now that $c_{x}(1-\delta_{\tau_{x},N})$ can be replaced by  $c_{x}-\delta_{\tau_{x},N}$, we finally have
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
	\end{split}
\end{equation} 
\begin{flushright}
    $\square$
\end{flushright}
\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 
\begin{equation}\label{ABS_1}
	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{(L+1-\sum_{x=1}^{L}c^{'}_{x})!}{(L+1)!}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}
\end{equation}
where we used the fact that 
\begin{equation}
	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\dt
\end{equation}
Equation \eqref{ABS_1} will be useful in the following. 
\end{remark}
\subsubsection{Closed formula for correlations}\label{correlation-section}
We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$. We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
\begin{equation}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
\end{equation}
We fix the dual configuration $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$, and we have 
\begin{equation}
	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})\dt
\end{equation}
Thus it follows that 
\begin{align}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle\dt
\end{align}
We denote by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$. Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$ defined in \eqref{bulkElementDualityMatrix} becomes
\begin{equation}
	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}
	\end{equation} then the following holds}
\begin{equation}
	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
\end{equation} 
\todo{double check and ref to $d_x$ and say that R is id}
{\color{blue}As a consequence we have that }
\begin{equation}
	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
\end{equation}
Therefore, it follows that, using the resolution of the identity
\begin{align}
\label{corr-psi1}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
	=&\sum_{\bm{\tau}\in \Omega^{'}}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\dt
\end{align}

@@

		\todo{can we remove q index in sum?}

@@

		\todo{?}

@@

The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$, {\color{blue}i.e. when only a type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations of SEEP: 

@@

\todo{double check}

@@

 \todo{?}

@@

\todo{?}

@@

\todo{is there $c_j$ and $c_k$ missing?}

@@

\appendix
\section*{Appendix}
\section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
$\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
\begin{align}
	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align}
\todo{what was Omega again?}
We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$. More explicitly, this dual configuration is given by
\begin{equation}
	\begin{cases}
		\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
		\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
	\end{cases}\dt
\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
\begin{align}\label{useful-InInterpretation}
	\Psi^{'}(\bm{\tau})=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align}
We observe that for any $x\in \{1,\ldots,L\}$
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
		%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		%	1\qquad  &\text{if}\quad \tau_{x}= N
		%	\end{cases}\dt
\end{equation}
Indeed, we have that 
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
		\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		1\qquad  &\text{if}\quad \tau_{x}= N
	\end{cases}\dt
\end{equation}
Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
\begin{equation}\label{interpretation-PsiP}
	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
\end{equation} 
This last equation completes and generalizes \eqref{corr-psi1} by showing that $\Psi^{'}(N,\ldots,N) =1$.

>>>>

@@

{\color{blue} \begin{remark}\label{reamrk-extraSite}
	In the following, with a slight abuse of notation, we denote the configuration vectors on the extra-site $u(x)$ by $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$. This allows to recall that these vectors belongs to the extra-space $N_{0}^{N-1}$ "attached" to original configuration space $\Omega$. Moreover, this notation allows to directly connect the ket-vector $|\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}\rangle$ with the row vector $(\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)})$ defined in \eqref{row-dual-vectors}, in which the components $\xi_{a}^{u(x)}$ denotes the number of dual particles of type $a$ at site $u(x)$.

@@

{\color{blue}With a slight abuse of notation and in the spirit of Remark \ref{reamrk-extraSite}, in equation \eqref{siteHadamardII}, we still denote the occupation vector at extra-site $u(x)$ by $\langle \xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}|$ although there is the summation over $\xi_{1}^{u(x)},\ldots,\xi_{N-1}^{u(x)}$.}

@@

where $\mathcal{P}_{x_1}(1)$ is the probability that a single random walk started at $x_1$ is absorbed {\color{blue}at site $0$}.\todo{site 0?} Then, using \eqref{exactCorrelations}, we have

@@

\todo{here Y instead of $\tau$? [DONE]}

@@

Therefore, we compute the third cumulant, i.e. the three-point connected correlation as 
\begin{align}
	&\mathbb{E}\left[\left(\mathbbm{1}_{\{Y_{x_{1}}=a_{1}\}}-\langle\rho_{a_{1}}^{x_{1}}\rangle \right)\left(\mathbbm{1}_{\{Y_{x_{2}}=a_{2}\}}-\langle\rho_{a_{2}}^{x_{2}}\rangle \right)\left(\mathbbm{1}_{\{Y_{x_{3}}=a_{3}\}}-\langle\rho_{a_{3}}^{x_{3}}\rangle \right)\right]\nonumber\\
	=&-\frac{2x_{1}(L+1-2x_{2})(L+1-x_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\dt
\end{align}
\todo{should this all be $Y$ in the identities?[DONE]}
\begin{remark} The first and second cumulants, computed in \eqref{one-pts-corr} and \eqref{two-pts-corr} respectively, match with those found in Section 4.3 of \cite{vanicat2017exact}.
	\end{remark}

@@

	\todo{added ref... What about Section 4.4.5?[PREVIOUS SECTION 4.4.5 NOW MOVED IN THE APPENDIX A]}

@@

Observing now that $c_{x}(1-\delta_{\tau_{x},N})$ can be replaced by  $c_{x}-\delta_{\tau_{x},N}$, we finally have
\begin{equation}\label{elementsABS}
	\begin{split}
		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
	\end{split}
\end{equation} 
\begin{flushright}
    $\square$
\end{flushright}
\begin{remark} By changing the summation indices from $c_x\in \{\delta_{\tau_{x},N},1\}$ to $c_{x}^{'}\in \{0,1-\delta_{\tau_{x},N}\}$ and by  the fact that occupation of each site is bounded by $1$ we rewrite \eqref{ABS} as 
\begin{equation}\label{ABS_1}
	\Psi^{'}(\bm{\tau})=\sum_{c^{'}_{1}=0}^{1-\delta_{\tau_{1},N}}\ldots\sum_{c^{'}_{L}=0}^{1-\delta_{\tau_{L},N}}\frac{(L+1-\sum_{x=1}^{L}c^{'}_{x})!}{(L+1)!}\prod_{x=1}^{L}\left((\alpha_{\tau_{x}}-\beta_{\tau_{x}})\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\right)^{c^{'}_{x}}\beta_{\tau_{x}}^{(1-c^{'}_{x}-\delta_{\tau_{x},N})}
\end{equation}
where we used the fact that 
\begin{equation}
	\left(1+\sum_{j=x}^{L}c_{j}\right) =\left(2+L-x-\sum_{j=x}^{L}c^{'}_{j}\right)\dt
\end{equation}
Equation \eqref{ABS_1} will be useful in the following. 
\end{remark}
\subsubsection{Closed formula for correlations}\label{correlation-section}
We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$. We fix $a_{k}\in\{1,\ldots,N-1\}$ and we would like to compute
\begin{equation}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right)\langle\bm{\tau}|\Psi\rangle\dt%=\sum_{\bm{\tau}\in \Omega^{'}}\left(\prod_{i=1}^{m}\mathbbm{1}_{\{\tau_{y_{i}}=s_{i}\}}\right)\Psi(\bm{\tau})
\end{equation}
We fix the dual configuration $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, corresponding to a vector $|\bm{\xi}\rangle$, and we have 
\begin{equation}
	\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}=D(\bm{\tau},\bm{\xi})\dt
\end{equation}
Thus it follows that 
\begin{align}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=&\sum_{\bm{\tau}\in \Omega^{'}}D(\bm{\tau},\bm{\xi})\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle\dt
\end{align}
We denote by $|\hat{\bm{\xi}}\rangle=|\xi^{1},\ldots,\xi^{L}\rangle$, i.e. the vector constructed from $|\bm{\xi}\rangle$ by removing the components at sites $0$ and $L+1$. Recalling that {\color{blue} in the case $\nu=1$, since the matrix $R_{x}$ defined in \eqref{Revmatrix} reduces to the identity, we have that the matrix $d_{x}$ defined in \eqref{bulkElementDualityMatrix} becomes
\begin{equation}
	d_{x}=\exp{(\sum_{a=1}^{N-1}e_{aN}^{x})}
	\end{equation} then, considering equation \eqref{transformationV}, the following holds}
\begin{equation}
	S_{1}^{T}=\prod_{x=1}^{L}d_{x}
\end{equation} 
\todo{double check and ref to $d_x$ and say that R is id [DONE]}
{\color{blue}As a consequence we have that }
\begin{equation}
	\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle=\langle \bm{\tau}|D|\bm{\xi}\rangle \dt
\end{equation}
Therefore, it follows that, using the resolution of the identity
\begin{align}
\label{corr-psi1}
	\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=& \sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|D|\bm{\xi}\rangle\langle\bm{\tau}|\Psi\rangle
	=\sum_{\bm{\tau}\in \Omega^{'}}\langle \bm{\tau}|S_{1}^{T}|\hat{\bm{\xi}}\rangle\langle\bm{\tau}|\Psi\rangle\nonumber\\
	=&\sum_{\bm{\tau}\in \Omega^{'}}\langle \hat{\bm{\xi}}|S_{1}|\bm{\tau}\rangle\langle\bm{\tau}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|S_{1}|\Psi\rangle
	=\langle \hat{\bm{\xi}}|\Psi^{'}\rangle\dt
\end{align}

@@

		\todo{can we remove q index in sum?[SUB-INDICES q REMOVED]}

@@

		\todo{?[EXPLAINED]}

@@

The computations made for the multispecies stirring process can be specialized to the single-species case $N=2$, {\color{blue}i.e. when only one type of particles and the holes are present.} In this situation we retrieve the SSEP, that was studied using the same approach as presented here in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations of SEEP: 

@@

\todo{double check [DONE]}

@@

 \todo{? [SENTENCE REWRITTEN]}

@@

\todo{?[BLUE SENTENCE REWRITTEN]}

@@

\todo{is there $c_j$ and $c_k$ missing?[DONE]}

@@

\appendix
\section*{Appendix}
\section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp}
We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
$\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
\begin{align}
	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align}
\todo{what was Omega again?[DONE]}
We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$. More explicitly, this dual configuration is given by
\begin{equation}
	\begin{cases}
		\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
		\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
	\end{cases}\dt
\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
\begin{align}\label{useful-InInterpretation}
	\Psi^{'}(\bm{\tau})=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align}
We observe that for any $x\in \{1,\ldots,L\}$
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
		%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		%	1\qquad  &\text{if}\quad \tau_{x}= N
		%	\end{cases}\dt
\end{equation}
Indeed, we have that 
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
		\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		1\qquad  &\text{if}\quad \tau_{x}= N
	\end{cases}\dt
\end{equation}
Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
\begin{equation}\label{interpretation-PsiP}
	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
\end{equation} 
This last equation completes and generalizes \eqref{corr-psi1} by showing that $\Psi^{'}(N,\ldots,N) =1$.
